---
title: "String practice"
author: "Haylee Oyler"
format: html
editor: visual
execute: 
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---

## Practice with strings

```{r}
# Use data pasta to read in df ----
rm(list = ls())
# library(datapasta)

alarm_report <- data.frame(
  stringsAsFactors = FALSE,
                              date = c("2020-03-14","2020-03-15","2020-04-10",
                                       "2020-04-18"),
                          building = c("Engineering-North","Bren Hall",
                                       "Engineering-South","Engr-North"),
                     alarm_message = c("10:02am -- HVAC system down, facilities management alerted",
                                       "8:24am -- Elevator North out of service",
                                       "12:41am -- Fire alarm, UCSB fire responded and cleared",
                                       "9:58pm -- Campus point emergency siren, UCPD responded")
                )
```
Practice working with strings by writing code to update alarm_report as follows (these can be separate, or all as part of a piped sequence):

Replace the “Engr” with “Engineering” in the building column
Separate the building column into two separate columns, building and wing, separated at the dash
Only keep observations with the word “responded” in the alarm_message column
Separate the message time from the rest of the message by separating at --
Convert the date column to a Date class using lubridate
```{r}
# String practice ----
alarm_report <- alarm_report %>% 
  mutate(building = str_replace(building, pattern = "Engr", replacement = "Engineering"))

# idk why this wouldn't work as one piped sequence. It would only do one mutate at a time, either change engineering of split the string
alarm_report <- alarm_report %>%
  mutate(building = str_split_fixed(alarm_report$building, "-", 2)[,1], 
         wing = str_split_fixed(alarm_report$building, "-", 2)[,2])

# str_split_fixed(alarm_report$building, "-", 2)[,2]

alarm_report <- alarm_report %>% 
  filter(str_detect(alarm_message, "responded")) %>%
  mutate(alarm_message = str_split(alarm_report$alarm_message, "--")) %>% 
  mutate(date = ymd(date))

# class(alarm_report$date)
```

